---
title: "Comcast Consumer Complaint Analysis"
author: "Midhun Mohan K"
date: "March 24, 2020"
output:
  html_document: default
  word_document: default
---
DESCRIPTION:
Comcast is an American global telecommunication company. The firm has been providing terrible customer service. They continue to fall short despite repeated promises to improve. Only last month (October 2016) the authority fined them a $2.3 million, after receiving over 1000 consumer complaints.
The existing database will serve as a repository of public customer complaints filed against Comcast.It will help to pin down what is wrong with Comcast's customer service.
Data Dictionary

•	Ticket #: Ticket number assigned to each complaint
•	Customer Complaint: Description of complaint
•	Date: Date of complaint
•	Time: Time of complaint
•	Received Via: Mode of communication of the complaint
•	City: Customer city
•	State: Customer state
•	Zipcode: Customer zip
•	Status: Status of complaint
•	Filing on behalf of someone

Import data into R environment.

```{r}
#Injesting the dataset into the R environment
setwd("/cloud/project")
getwd()
cust_com = read.csv("Comcast Telecom Complaints data.csv",stringsAsFactors = T)
#view(cust_com)
str(cust_com)

```

From the above output, it is conclusive that the 'Date' variable with 'Factor' Data type will affect the analysis. We therefore change it's datat type to R Date Data Type for further analysis.
```{r}
#Data Cleaning
#Converting Dates into R Date Type
##install.packages("lubridate")
library(lubridate) 
mdy = mdy(cust_com$Date)
dmy = dmy(cust_com$Date)
mdy[is.na(mdy)] <- dmy[is.na(mdy)]
cust_com$Date = mdy

#Verifying for change in Date Datatype
str(cust_com$Date)

```

Number of complaints at monthly and daily granularity levels.

Daily Trend Chart.
```{r}
#install.packages("dplyr")
library(dplyr)
library(ggplot2)
library(scales)


#Daily Trend Chart
comp_dates=data.frame(cust_com$Date)
colnames(comp_dates)=c("Dates")
comp_dates=comp_dates %>% group_by(Dates) %>% summarise(frequency = n())

str(comp_dates)
figure_1 <- ggplot(comp_dates, aes(Dates, frequency)) + geom_line()+
  scale_x_date(date_labels = "%d/%m/%y",date_breaks = "1 day")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
figure_1
```

Monthly Trend Chart
```{r}
##install.packages("tidyverse")
library(tidyverse)
com_months=data.frame(comp_dates)
##view(b)
colnames(com_months)=c("Months")
com_months=month(com_months$Months)
str(com_months)
com_months=as.data.frame(com_months)
com_months <- transform(com_months,MonthAbb = month.abb[com_months])
com_months=com_months$MonthAbb
#view(com_months)
levels(com_months)
com_months=as.data.frame(com_months)
com_months=com_months %>% group_by(com_months) %>% summarise(frequency = n())
str(com_months)
barplot(com_months$frequency,names.arg = com_months$com_months)
```

Frequency of complaint types.

```{r}
#Frequency of Complaint Types
##install.packages("tm")
##install.packages("wordcloud")
library(tm)
library(wordcloud)
###view(cust_com)

complaint_list = data.frame(cust_com$Customer.Complaint)
colnames(complaint_list)=c("Complaint")
###view(complaint_list)
corpus= Corpus(VectorSource(complaint_list$Complaint))

corpus [[2]][1]
#Text Cleaning

#Converting all text into lower case

corpus <- tm_map(corpus,content_transformer(tolower))
corpus [[2]][1] #Everything turned to lower case
#Remove Numbers
corpus<- tm_map(corpus,removeNumbers)

corpus[[4]][1] # There was a number before line execution

#Removing common stop words
corpus = tm_map(corpus,removeWords,stopwords(kind="en"))

corpus[[4]][1] # Words like 'a' 'the' of got removed

#Remove Punctuation
corpus = tm_map(corpus,removePunctuation)

#Removing white spaces
corpus = tm_map(corpus,stripWhitespace)
corpus[[4]][1]

#Remove additional words

corpus= tm_map(corpus,removeWords,c("get","took","can","can","comcast"))

#Create Term Document Matrix (TDM)

tdm = TermDocumentMatrix(corpus)
m=as.matrix(tdm)
v=sort(rowSums(m),decreasing = T)
#List with Frequency of Compliant Types
d=data.frame(word=names(v),freq=v)

head(d)
```

```{r}
set.seed(2)
wordcloud(d$word,d$freq,random.order=F,min.freq = 1,rot.per =0,scale = c(4,.5),max.words = 100,colors = brewer.pal(8,"Dark2"))
title(main = "Complaint Types - Word Cloud",font.main=1,cex.main=1.5)
```
Creating a new categorical variable with value as Open and Closed. Open & Pending is to be categorized as Open and Closed & Solved is to be categorized as Closed.
```{r}
#Now we convert the Data Frame c$Status into a categorical Variable
cust_com$Status=as.character(cust_com$Status)
cust_com$Status[cust_com$Status %in% c("Open","Pending")] <- "Open"
cust_com$Status[cust_com$Status %in% c("Closed","Solved")] <- "Closed"
cust_com$Status=as.factor(cust_com$Status)
levels(cust_com$Status)
```
State wise status of complaints in stacked bar chart
```{r} 
#Making a Frequency Data Frame by State
c=data.frame(cust_com$State,cust_com$Status)
str(c)
summary(c)
c
c_tac=table(c)
c_tac
###view(c_tac)
c_pok=data.frame(c_tac)
c_pok
colnames(c_pok)=c("States","Status","Frequency")
##view(c_pok)
#str(c_pok)
#States with Maximum Complaints
##install.packages("viridis")
##install.packages("hrbrthemes")
library(ggplot2)
library(viridis)
library(hrbrthemes)
ggplot(c_pok,aes(fill=Status,x=Frequency,y=States),)+
  geom_bar(position="stack", stat="identity") +
  scale_fill_viridis(discrete = T) +
  ggtitle("Complaint Status by State") +
  theme_ipsum() +
  xlab("Count")
```
States with Maximum Complaints
```{r}
max_comp <- data.frame(cust_com$State)
max_comp=max_comp %>% group_by(cust_com.State) %>% summarise(frequency = n())
colnames(max_comp)=c("States","Freq")
max_comp=max_comp[order(max_comp$Freq,decreasing = T),]
head(max_comp)
```
States with highest percentage of Unresolved Complaints
```{r}
unresol_comp=data.frame(c_pok[44:86,])
rownames(unresol_comp)=c_pok$States[44:86]
colnames(unresol_comp)=c("State","Status","Freq")
##view(unresol_comp)
unresol_comp$Per= (unresol_comp$Freq/sum(unresol_comp$Freq))*100

unresol_comp=unresol_comp[order(unresol_comp$Per,decreasing = T),]
unresol_comp$Per =format(unresol_comp$Per,digits=2)
head(unresol_comp)
```


Provide the percentage of complaints resolved till date, which were received through theInternet and customer care calls.

```{r}
com_res_td = data.frame(cust_com$Received.Via)
colnames(com_res_td)= c("Received Via")
com_res_td=com_res_td %>% group_by(`Received Via`) %>% summarise(frequency = n())
com_res_td$Percentage =  percent(com_res_td$frequency/2224)
com_res_td

```

